### 2020-03-06 README.Rmd
small updates to readme

# timeternR <img src="man/figures/logo.png" align="right" alt="" width="120" />

@@

```{r}
n_sims <- 100
n_time_steps <- 100
beta <- .1
gamma <- .03
init_SIR <- c(950, 50, 0)
output_format <- "data.frame"

>>>>

# EpiCompare <img src="man/figures/logo.png" align="right" alt="" width="120" />

@@

```{r eval = F}
n_sims <- 100
n_time_steps <- 100
beta <- .1
gamma <- .03
init_SIR <- c(950, 50, 0)
output_format <- "data.frame"
